{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras

### 2011-05-27 doc/paper.tex
First premature pictures in the paper. Some optimisation of affine.m

We have made some experiments with our implementations of Freudenthal formula and formula \eqref{eq:15} and have got the following graphs \ref{freudenthal-racah-times}.

@@

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

>>>>

We have made some experiments with our implementations of Freudenthal formula and formula \eqref{eq:15} and have got the following graphs \ref{freudenthal-racah-times}.
\begin{figure}[h]
  \label{freudenthal-racah-times}
  \noindent\centering{
    \includegraphics[width=80mm]{timing.pdf}
  }
  \caption{Running time of algorithms based on recurrent formula \eqref{eq:15} (in blue) and \eqref{eq:14} (in red) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
\end{figure}

@@

\begin{figure}[h]
  \label{branching-b4-b2}
  \noindent\centering{
    \includegraphics[width=80mm]{branching.pdf}
  }
  \caption{Branching coefficients of module $L^{\left[0,1,0,2\right]}$ for regular embedding $B_{2}\subset B_{4}$ displayed in the basis $\left\{e_3,e_4\right\}$}
\end{figure}

@@

\newpage
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix
